Red Oak: Something Something Algorithmic Policy

### 2015-05-06 draft.tex
..

\section*{Decision Trees and Algorithmic Policies}
   \subsection*{Range-based Branching}
   % Why range instead of actual value, pre-generation of rules using symbolic pre-execution

@@

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)

@@

   \subsection*{Combining Algorithmic Policies}
   % cross, ``holes''

>>>>

\section*{Decision Trees and Algorithmic Policies}

   \subsection*{Range-based Branching}
   % Why range instead of actual value, pre-generation of rules using symbolic pre-execution

@@

@@

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)
   Under the big switch model, the forwarding decisions returned by algorithmic policies are destination-based rather than path-based. For example, the algorithmic policy may decide to deliver a packet, at which point this interpretation will be interpreted as forwarding a packet along a path terminating at the packet's destination. Packets may also be dropped, or forwarding to a static location. Our model also allows for dynamic forwarding based on component of relation, for example to the last seen location of a host according to a MAC-learning controller.

   \subsection*{Combining Algorithmic Policies}
   % cross, ``holes''
   As algorithmic policies under our model are functions of the host language, we inherit the latter's function space ability, allowing, amongst other things, for compositon of algorithmic policies and higher-order algorithmic policies.

\begin{figure}[ht]
\begin{lstlisting}

let filter_src_range  (f: packet -> forwarding_decision) (r:range) (pkt: packet) : forwarding_decision =
 if in_range pkt IpSrc r then
    f pkt
 else
   Drop   
\end{lstlisting}

\caption{Example of a Partial Algorithmic Policy}
\label{fig:ex-hole}
\end{figure}

   For example, we include in Figure~\ref{fig:ex-hole} the source code for \lstinline|filter_src_range| a partial algorithmic policy which, given an algorithmic policy \lstinline|f| and a range \lstinline|r|, will forwards all packets whose source IP is within range \lstinline|r| and drop the packet otherwise.

   \begin{figure}[ht]
\begin{lstlisting}
let f_cross (f_1) (f_2) pkt =
  let d_1 = f_1 pkt in
  let d_2 = f_2 pkt in
  Multicast (d_1,d_2)
\end{lstlisting}

\caption{Example of a Composition Operator}
\label{fig:ex-cross}
\end{figure}

Various composition operator may be built as host language function to combine multiple algorithmic policies into a single one. For example, \lstinline|f_cross|, included in Figure~\ref{fig:ex-cross}, runs algorithmic policy \lstinline|f_1| and \lstinline|f_2| on input packets and multicast them according to both forwarding decisions.
